Sequential Composition for Relaxed Memory: Pomsets with Predicate Transformers

### 2021-06-17 paper/2SUB/outro.tex
reorg

This paper is the first to present a direct compositional semantics for
sequential composition in a relaxed memory model which can be
efficiently compiled to modern CPUs. There is, as usual, more research
to be done.

@@

>>>>

This paper is the first to present a direct denotational semantics for
sequential composition in a relaxed memory model which can be
efficiently compiled to modern CPUs. There is, as usual, more research
to be done.

@@

We don't handle access elimination.
